Conductive and convective heat transfer in inductive heating of subsea buried pipelines

### 2021-10-08 manuscript.tex
:pencil: Abstract

% Please include an abstract:
\begin{abstract}
%The abstract should be a single paragraph (150-175 words long) 
\end{abstract}

@@

\begin{figure}[htbp]
    \centering
    \includegraphics[width=\linewidth]{figs/model.pdf}
    \caption{Schematic of the simulation geometry (not to scale). A fine mesh size of 0.004 m was used to discretize the domain with 250,000 elements.}
    \label{fig:model}
\end{figure}

>>>>

% Please include an abstract:
\begin{abstract}
Inductive heating with high-voltage cables reduces the risk of hydrate formation by raising the temperature of the production fluid in the pipeline. Inductive heating loses heat to the surrounding soil through conduction or convective flow through the soil. However, the amount of heat lost in conduction or convection and the transition from conduction to convection remains unknown. Soil permeability, cable temperature, and burial depth influence the mode of heat transfer and the amount of heat lost. We study the different modes of heat transfer of pipelines with inductive heating using 2D Finite Difference analysis. Low permeability soil only experiences conductive heat transfer, thus losing minimum heat to the surrounding soil. In contrast, convective flow drives the heat away from the pipeline and towards the ground surface for highly permeable soils, barely heating the fluid.  We identify a critical Rayleigh-Darcy number of 1 as the controlling value separating conduction and convective heat dissipation. An increase in burial depth deteriorates the heating efficiency of convective regions (high permeability soils), while the heating efficiency in the conduction-dominated low permeability soils remains unaffected.
\end{abstract}

@@

\begin{figure}[htbp]
    \centering
    \includegraphics[width=0.7\linewidth]{figs/model.pdf}
    \caption{Schematic of the simulation geometry (not to scale). A fine mesh size of 0.004 m was used to discretize the domain with 250,000 elements.}
    \label{fig:model}
\end{figure}
